The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-12 article.tex
Refs in intro

The computational tools a contemporary phylogeneticist has at his/her disposal
goes beyond the wildest imagination of those living two decades ago. 
Advances in computational power allowed the first cladograms to be inferred 
from DNA alignments in [some year, some ref]. The first time-trees were
published in [some year, some ref]. Thanks to the addition of effective sampling
methods, the first Bayesian tools appeared in [some year, some ref], allowing
for unprecedented flexibility in the setup of a phylogenetic model.

Currently, the most popular Bayesian phylogenetics tools are BEAST [ref],  
MrBayes [ref] and RevBayes [ref]. Each of these use efficient tree sampling 
routines to create a posterior probability distribution of the to-be-inferred 
phylogenetic tree. But next to the computational speed, they also allow
to incorporate known or hypothesized structure of the phylogenetic 
tree-to-be-inferred through the model priors.

>>>>

The computational tools a contemporary phylogeneticist has at his/her disposal
goes beyond the wildest imagination of those living two decades ago. 
Advances in computational power allowed the first cladograms to be inferred 
from DNA alignments in 1981 \cite{felsenstein1981}. The first Bayesian tools 
appeared in 1996 \cite{rannala1996}, allowing
for unprecedented flexibility in the setup of a phylogenetic model.

Currently, the most popular Bayesian phylogenetics tools are BEAST \cite{beast},  
MrBayes [ref] and RevBayes [ref]. Each of these use efficient tree sampling 
routines to create a posterior probability distribution of the to-be-inferred 
phylogenetic tree. But next to the computational speed, they also allow
to incorporate known or hypothesized structure of the phylogenetic 
tree-to-be-inferred through the model priors.
